Exploratory Plots

### 2023-12-20 Code/R/RMarkdown/EntropyPlots.Rmd
code test

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(linetype = "longdash",  linewidth = 0.8) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "blue", linetype = "dashed", size = 1) + 
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")

>>>>

ggplot(muEntropy.molten, aes(x = mu, y = Entropy, col = alpha)) +
  geom_line(data = Entropy_gamma.molten, aes(x = mu, y = `Entropy Gamma`), color = "black", linetype = "solid", size = 1) + 
  geom_line(linetype = "longdash",  linewidth = 1.5, alpha=.7) +
  annotate("text", x = max(mu)+0.2, y = max(Entropy_gamma.molten$`Entropy Gamma`), 
           label = TeX("$\\Gamma_{\\tiny{SAR}}$"), vjust = 0.9, hjust = 0.1, color = "blue")+
  theme_minimal() +
  #scale_color_manual(values =  rainbow(7)[1:5], labels = alpha_labels) +
  scale_color_manual(values = pal_jama()(7)[1:5], labels = alpha_labels) +
  #scale_color_manual(values = 	pal_cosmic()(7)[1:5], labels = alpha_labels) +
  labs(col = "Roughness", linetype = NULL) +
  xlab(expression(paste(mu))) +
  ylab("Entropy") +  
  theme(text = element_text(family = "serif"),
        legend.position = "bottom")
